---
title: "Week6b Lab: Using ChemData"
author: "Caroline"
date: "`r Sys.Date()`"
output: 
  html_document:
    toc: TRUE
    toc_float: TRUE
---

```{r setup, include=FALSE, echo=FALSE}
knitr::opts_chunk$set(echo = TRUE,
                      warning=FALSE, 
                      message=FALSE,
                      fig.path = "../output/") #adding the path directory
```

# **Quick Summary**

Here we will be using the Chemical Data from *Week 4* and will be following these steps:
 
  1. Load the libraries needed to use specific functions 
  2. Load the data that we will be using throughout this script  
  3. Create a plot that focuses on the Temp and Salinity per zone  
  4. Create a table looking at the mean of Salinity per zone  

# **Loading Data**

### *Load Libraries*

These are the libraries that will be needed for this script:

```{r}
library(tidyverse)
library(here)
library(kableExtra)
```

### *Load ChemData*

This is the data that we will be using for this script. Note that we will also be filtering out any incomplete rows in our data:
    
```{r}
ChemData<-read_csv(here("Week_04","data", "chemicaldata_maunalua.csv"))

ChemData_clean <- ChemData %>%
  filter(complete.cases(.)) #filters out everything that is not a complete row
```

This is just to visualize a summary of the data:

```{r ChemData_clean}
summary(ChemData_clean) #summary of data
```
# **Plot and Table**

### *Create Plot*

Now we are creating our plot by calling our filtered data and setting all the different parameters:

```{r chem_data_clean_plot, fig.align="center", fig.asp=1.2, fig.cap="Plots by Temp v Salinity; grouped by Zone v Tide Time"}
ChemData_clean %>% #calling updated chemdata
  ggplot(aes(x = Temp_in, #setting x and y axis to temp and salinity
             y = Salinity,
             color = Zone)) + #basing color by Zone
geom_point() +
  labs(x = "Temperature", # x and y labels
       y = "Salinity",
       color = "Zone") +
  theme_bw() +
  facet_grid(Zone~Tide_time) #facet grid by zone and tide time
```

### *Create Table*

Creating a table to better visualize the mean of salinity by zone:

```{r fig.cap="Table showing the mean of Salinity grouped by Zone"}
ChemData_clean %>% # calling data
  group_by(Zone) %>% # group by zone
  summarise(Mean = mean(Salinity, na.rm = TRUE)) %>% # summarise the mean of sal
  kbl()  %>% # make it a kable table
  kable_classic()%>% #theme
  row_spec(2, bold = T, color = "black", background = "lightgrey") %>% #choose column to change 
   kable_styling(full_width = FALSE) #automatically change to fit text
```


