---
title: "week 12b lab: forloops and purrr"
author: "Caroline S."
date: "`r Sys.Date()`"
output: 
  html_document:
    toc: TRUE
    toc_float: TRUE
---

```{r setup, include=FALSE, echo=FALSE}
knitr::opts_chunk$set(echo = TRUE,
                      warning=FALSE, 
                      message=FALSE,
                      fig.path = "../output/") #adding the path directory
```

# Instructions

Each of these files is a timeseries of temperature and light data collected in tide pools in Oregon by Jenn Fields. Your goal is to bring in all 4 files and calculate the mean and standard deviation of both temperature (Temp.C) and light (Intensity.lux) for each tide pool. Use both a for loop and map() functions in your script. (Basically, do it twice). Due Tuesday at 1pm.

## Libraries

```{r}

library(tidyverse)
library(here)

```

# Forloop Section

## Load data for Forloop

Here I load the same data with a format that works for the forloop

```{r}

  # point to the location on the computer of the folder
  HomePath<-here("Week_12", "data", "homework")
  # list all the files in that path with a specific pattern
  # you can use regex to be more specific if you are looking for certain patterns in filenames
  files <- dir(path = HomePath,pattern = ".csv") #looking for everything that has a .csv in the filename
  files
```



## Functions for Forloop:

### Create Empty Dataframe
here we make an empty data frame to place the the requested data in

```{r}
# pre-allocate space
  # make an empty dataframe that has one row for each file and 5 columns
  home_data<-data.frame(matrix(nrow = length(files), ncol = 5))
  # give the dataframe column names
  colnames(home_data)<-c("filename","mean_temp", "mean_light","sd_temp", "sd_light") #create col names
  home_data
  
  raw_data<-read_csv(paste0(HomePath,"/",files[1])) # test by reading in files
  head(raw_data)
```
###Create forloop
Here I create the actual forloop

```{r}
for (i in 1:length(files)){ # loop over 1:4 the number of files by using i index
    raw_data<-read_csv(paste0(HomePath,"/",files[i]))
    #glimpse(raw_data)
    home_data$filename[i]<-files[i]
    home_data$mean_temp[i]<-mean(raw_data$Temp.C, na.rm =TRUE) #mean of temp
    home_data$mean_light[i]<-mean(raw_data$Intensity.lux, na.rm =TRUE) #mean of light
    home_data$sd_temp[i]<-sd(raw_data$Temp.C, na.rm =TRUE) #standard dev of temp
    home_data$sd_light[i]<-sd(raw_data$Intensity.lux, na.rm =TRUE) #standard dev of light
  } 
  home_data
#write.csv(HomePath,here("data","homework","forloop_data"), row.names=FALSE)
```


# Purrr Section

## Load same data for Purrr:

Here we are formatting the data so we can use it for purrr

```{r}
  # point to the location on the computer of the folder
  HomePath<-here("Week_12", "data", "homework")
  files <- dir(path = HomePath,pattern = ".csv", full.names = TRUE)
  #save the entire path name
  files
```

## Functions for Purrr

### calculate the means and standard deviation
Here we are data wrangling and calculating the means and standard deviation
```{r}
  
  #calculate means and standard deviation
  pur_data<- files %>%
    set_names() %>% # set's the id of each list to the file name
    map_df(read_csv,.id = "filename") %>% # map everything to a dataframe and put the id in a column called filename
    group_by(filename) %>%
    summarise(mean_temp = mean(Temp.C, na.rm = TRUE), #mean for temp
              mean_light = mean(Intensity.lux,na.rm = TRUE), #mean for light
              sd_temp = sd(Temp.C, na.rm = TRUE), #stand dev for temp
              sd_light = sd(Intensity.lux,na.rm = TRUE)) #stand dev for light
  pur_data
  
```  
